Notebook: Predictors of frog survival following translocation

### 2022-03-07 doc/notebook/notebook_translocation.Rmd
Edits related to switch to github_document format

---
title: "Translocation notebook"
author: "Roland Knapp"
date: "`r Sys.Date()`"
output:
  html_document
---

@@

## Predictors of frog survival following translocation

### Dataset structure

@@

### Model structure

@@

>>>>

---
title: "Notebook: Predictors of frog survival following translocation"
author: "Roland Knapp"
date: "`r Sys.Date()`"
output:
  github_document: 
    toc: true
---

@@

## Dataset structure

@@

## Model structure

@@

## Results

To be added soon.
